---
title: "README"
author: "Yifu Yan"
date: "3/11/2019"
output: 
    md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 1.Usage of `mutate_all()`, `mutate_if()` and `mutate_at()`

Use scoped variants of `summarise()`, `mutate(`) and `transmute()` when handling many columns. 

1. `.predicate`:
    1. `_at()` variants accepts `vars()` for selecting columns.
    1. `_if()` variants accepts logical conditions for selecting columns.
1. `.funs`:
    1. Use `funs()`, which support renaming new columns
    2. Use function name(e.g. sum,mean)
    3. Use purrr syntax(`~.x`)

```{r}
library(dplyr)
library(rlang)
```


Instead of doing:

```{r}
mtcars %>%
    group_by(cyl) %>%
    transmute(mpg_sum = sum(mpg),
           disp_sum = sum(disp),
           mpg_pct = mpg/sum(mpg),
           disp_pct = disp/sum(disp)) %>%
    head() %>%
    knitr::kable()
```


Do:

```{r}
mtcars %>%
    group_by(cyl) %>%
    transmute_at(vars(mpg,disp),
              funs(sum = sum(.),
                   pct = ./sum(.))) %>%
    head() %>%
    knitr::kable()
```

## 2.Programming with dplyr(symbols, expressions, quosures and strings conversion and evaluation)

When Programming with **tidyverse/dplyr/ggplot**, Sometimes we need conversion between symbols, expressions, quosures and strings. It can be really annoying if we don't know what to do. Luckily,with `rlang` package, we can perform these calculations easily.

```{r include=FALSE}
library(dplyr)
library(rlang)
```

Based on my personal understanding the difference between them are:

```{r echo=FALSE}
tribble(
    ~ Type, ~ `How to Create`, ~ Notes,
    "string", 'var <- "a"', "",
    "symbols", "symbol1 <- sym('a');", "Convert string to symbol",
    "expression", "expr1 <- expr(a + 1)", "Expression will not be evaluated until using `eval_tidy()`",
    "quosure", "quo1 <- quo(a + 1)", "Quosure has its original environment attatched, it will always be evaluated in attached environment"
) %>%
    knitr::kable()
```


## Tidy Evaluation in global environment 

### `sym` and `syms`

`sym` and `syms` Convert string(s) to symbol(s).

#### Singular

```{r}
myvar <- 1
# Convert string to symbol
sym("myvar")
# Evaluate
eval_tidy(sym("myvar"))
```

#### Plural

```{r}
myvar1 <- 1
myvar2 <- 2
# convert strings to symbols
syms(list("myvar1","myvar2"))
# evaluate
purrr::map(syms(list("myvar1","myvar2")),eval_tidy)
```

#### Assignment

##### Singular assignment using  `sym()` and `eval_bare()`/`base::eval()`/`env_bind()`/`assign()`

```{r}
var_name <- "a"
var_value <- "myvalue"

# construct assignment expression
myexpr <- call2("<-",sym(var_name),var_value)
myexpr

# evaluate ----
invisible(eval_bare(myexpr)) # eval_bare prints to console, so use invisible to hide it
# or 
eval(myexpr) # this works the same way
# or
env_bind(current_env(),!!sym(var_name) := var_value)
# or
assign(var_name,var_value) # sym() is not needed in this case

a
```

##### Assignment using `sym()` and `eval()`

### `expr` and `exprs`

`expr` and `exprs` presrve expressions, it will be evaluated only when evaluated with `eval_tidy()`

```{r}

expr1 <- expr(a + 1) # a hasn't be defined yet
# Expression
expr1

# Evaluate
a <- 1
eval_tidy(expr1)


```

```{r}
my_expres <- exprs(a+1,b+1)
# expressions
my_expres

# evaluate
a <- 1 
b <- 2
purrr::map(my_expres,eval_tidy)
```

**Assign values using expression**

```{r}

```


### `quo` and `quos`